tstrait: a quantitative trait simulator for ancestral recombination graphs

### 2024-03-13 paper.tex
Fix figure
Updates from Overleaf

\section{Acknowledgments}
We are grateful to Gregor Gorjanc, Ben Haller, Ben Jeffery and
others in the tskit community for helpful discussions and feedback.

@@

\clearpage

@@

\begin{figure}[t]%
\centering
% FIXME get the sizes right here and in the notebook where we're generating
% the figure so we don't have to scale here.
\includegraphics[width=\columnwidth]{figures/computational-time-code/stdpopsim-time.pdf}
\caption{Time taken to simulate quantitative traits with increasing
sample size. For each sample size, we simulated an ARG under human-like
parameters using the default HomSap demographic model in \texttt{stdpopsim}.
Each point represents the mean time for 10 independent runs of \texttt{tstrait}
for a particular ARG. The times reported are the total CPU
time required to simulate a quantitative trait with 1000 causal sites,
on an Intel(R) Core(TM) i9-11900H CPU and 16 GB of RAM.
The trait model is a normal distribution with $\mu=0$,
$\sigma^2=1$, $h^2=0.3$, and $\alpha=0$.
}\label{fig:time}
\end{figure}
\end{document}

>>>>

\section{Acknowledgments}
We are grateful to Gregor Gorjanc, Ben Haller, Ben Jeffery, Pier Palamara, Alison Etheridge and
others in the tskit community for helpful discussions and feedback.

@@

%\clearpage

@@

\begin{figure}[h]%
\centering
% FIXME get the sizes right here and in the notebook where we're generating
% the figure so we don't have to scale here.
\includegraphics[width=\columnwidth]{figures/stdpopsim-time.pdf}
\caption{Time taken to simulate quantitative traits with increasing
sample size. For each sample size, we simulated an ARG under human-like
parameters using the default HomSap demographic model in \texttt{stdpopsim}.
Each point represents the mean time for 10 independent runs of \texttt{tstrait}
for a particular ARG. The times reported are the total CPU
time required to simulate a quantitative trait with 1000 causal sites,
on an Intel(R) Core(TM) i9-11900H CPU and 16 GB of RAM.
The trait model is a normal distribution with $\mu=0$,
$\sigma^2=1$, $h^2=0.3$, and $\alpha=0$.
}\label{fig:time}
\end{figure}
\end{document}
